XP-C General Read Sequence Figure Generation

### 2022-06-01 R/XP-CDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added XP-C notebooks

---
title: "CS-B Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "CS-B"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "XP-C Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

### 2022-06-01 R/XP-CDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added XP-C notebooks

---
title: "CS-B Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "CS-B"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)

>>>>

---
title: "XP-C Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

### 2022-06-01 R/XP-CDeaminationSequenceAndPositionDataGeneration.rmd
Added XP-C notebooks

---
title: "CS-B Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "CS-B"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
expansionOffset = 0
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "XP-C Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 0
cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

### 2022-06-01 R/XP-CDeaminationSequenceAndPositionFigureGeneration.rmd
Added XP-C notebooks

---
title: "CS-B Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "CS-B"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "XP-C Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

### 2022-06-01 R/XP-CGeneralReadSequenceDataGeneration.rmd
Added XP-C notebooks

---
title: "CS-B General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

>>>>

---
title: "XP-C General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

### 2022-06-01 R/XP-CGeneralReadSequenceFigureGeneration.rmd
Added XP-C notebooks

---
title: "CS-B General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

>>>>

---
title: "XP-C General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---
